Assistant Tools and Accessibility Features for Blind People Playing Visual-Centric Digital Games

### 2024-02-16 Paper/paper.tex
improved structure and started with the section "The Details"

	In this work we go deeper into different and potentially new accessibility features as well as what assistant tools blind players use and how software companies implement them.
	This raises two relevant research questions (RQ):

	\begin{itemize}
		\item RQ1: What new breakthrough accessibility features and tools could enhance the gaming experience for blind players?
		\item RQ2: How can the development and implementation of these features and tools be standardized within the development cycle of visual-centric digital games?
	\end{itemize}

@@

	\begin{itemize}
		\item Audio Cues and Descriptions
		\item Text-to-Speech (TTS) and Voiceover
		\item Navigation Aids and Wayfinding Tools
		\item Comprehensive Audio Design
		\item Customizable Controls and Inputs
		\item Tactile Feedback and Controller Design
	\end{itemize}

@@

    To address the environment and pathfinding problems, one new technology was introduced in 2018 by \textcite{andrade_echo-house_2018} to use echolocation to explore a virtual environment which could drastically improve navigation in it.
    As for perspective (camera) and interacting with the world, hardware solutions like haptic feedback or AI assistant tools could be a solution when developed and integration further.
    Whereas the haptic feedback of e.g. PS5-Controllers could indicate when players aim too high or too low and the AI-Tool could provide the player with enhanced audio descriptions how to interact with the world.

    In summary, it can be said that the game industry already takes into account the most important accessibility features, yet most modern visually-centric digital games are still a major challenge for blind players.
    In the following section we will delve deeper into the listed features above, their problems and possible solutions, as well as how to improve the overall experience of blind people.

	\section{The Details}

	Subsections for the details section
	\begin{itemize}
		\item Universally accessible game design
		\item Problems implementing accessibility features in digital games
		\item Cost effective methods to implement accessibility features
		\item Improve exploring virtual environments using echolocation
	\end{itemize}

	%TODO
	New tools for blind players and newest Accessibility Features software companies using/developing.

	Screen Reader
	Audio Cues and Descriptions
	Haptic Feedback
	Customizable Controls
	Text-to-Speech and Speech Recognition
	Accessible Menus and Interfaces
	Echolocation

	Provide a detailed explanation of how your idea will be implemented. This section should delve into the technical aspects of your proposed solution and address any challenges or limitations that may arise. Consider including the following information:

	The specific features and functionalities of your assistant tools or accessibility features.
	The technologies or algorithms involved in implementing these features (e.g., machine learning, computer vision).
	Any hardware or software requirements necessary for your solution to work.
	How your solution will be integrated into existing digital games or gaming platforms.
	Any user testing or feedback you have conducted to validate your idea.

	\section{Related Work}
	%TODO
	Review existing literature and research related to assistant tools and accessibility features for blind gamers. This section should provide an overview of the current state-of-the-art in this field and highlight any relevant studies or projects. Consider addressing the following points:

	Previous research on accessibility features in digital games for blind players.
	Existing assistant tools or software developed to improve the gaming experience for blind individuals.
	Studies or projects that have investigated the challenges faced by blind gamers and potential solutions.
	Any notable advancements or innovations in the field of accessibility technology for blind users.
	How your research builds upon or contributes to the existing body of work in this area.

	\section{Conclusions and Further Work}
	What else could be done, explored deeper or would benefit blind players
	%TODO
	Summarize the key findings and contributions of your research paper. Reflect on the significance of your proposed idea and its potential impact on improving accessibility for blind gamers. Additionally, discuss any avenues for future research or development in this field. Consider addressing the following points:

	A recap of the problem addressed and the proposed solution.
	The implications of your research for the gaming industry and the broader accessibility community.
	Any remaining challenges or unanswered questions that need to be addressed.
	Suggestions for future research directions or enhancements to your proposed idea.
	How your work contributes to advancing the state-of-the-art in accessibility technology for blind individuals playing digital games.

>>>>

	Implementing accessibility features is much needed in digital games to ensure that everyone can enjoy gaming.
	However, game developers in general face various problems in the process of developing games, some of them are:

	\begin{itemize}
		\setlength\itemsep{0.5em}
		\item Diverse Needs
		\item Technical Challenges
		\item Design Compromises
		\item Standardization
	\end{itemize}

	In this study, we explore different and innovative accessibility features and tools, including haptic feedback which is a major technical challenge, design compromises and their associated problems and the need for standardization.
	This raises two relevant research questions (RQ):

	\begin{itemize}
		\setlength\itemsep{0.5em}
		\item RQ1: Which innovative accessibility features and tools can enhance the gaming experience for blind players?
		\item RQ2: In what ways can haptic feedback enhancements improve the game experience for blind players?
	\end{itemize}

@@

	\begin{itemize}
		\setlength\itemsep{0.5em}
		\item Audio Cues and Descriptions
		\item \emph{Text-to-Speech} (TTS) and Voiceover
		\item Navigation Aids and Wayfinding Tools
		\item Comprehensive Audio Design
		\item Customizable Controls and Inputs
		\item Tactile Feedback and Controller Design
	\end{itemize}

@@

    To address the environment and pathfinding problems, one new technology was introduced in 2018 by \textcite{andrade_echo-house_2018} to use echolocation to explore a virtual environment which could drastically improve navigation in it.
    As for perspective (camera) and interacting with the world, hardware solutions like haptic feedback or AI assistant tools could be a solution when developed and integration further.
    Whereas the haptic feedback \cite{bello_haptics_2016} of for example PS5-Controllers \cite{akyaman_anticipated_2021, chen_gamepad_2024} could indicate when players aim too high or too low while the AI-Tool could provide the player with enhanced audio descriptions and how to interact with the world.

    In summary, it can be said that the game industry already takes into account the most important accessibility features, yet most modern visually-centric digital games are still a major challenge for blind players.
    In the following section we will delve deeper into some of the listed features above, their problems and possible solutions, as well as how to improve the overall experience of blind people.

	\section{The Details}
	In this section, we delve into enhancing accessibility in digital games for blind players.
	Firstly, we aim to explore previously mentioned developing problems, from universally accessible game design affecting diverse needs followed by technical challenges.
	Secondly, we propose enhancements of already existing accessibility features in the theme environment navigating.
	Lastly, we explore various types of feedback which are essential in enhancing of accessibility in digital games and focus on haptic feedback as well as further possibilities to use that to improve the experience in digital games for blind players.

	\subsection{Universally accessible game design}
	%TODO
	Test

	\subsection{Navigate a virtual environment using echolocation}
	%TODO
	Test

	\subsection{Assistive haptic feedback}
	%TODO
	Short introduction into feedback variants and where it is used "visual perception (sight), haptics (tactile) and aural (hearing)". \cite{kuber_towards_2007}

	\subsection{Further possibilities to use haptic feedback}
	%TODO
	Test

	\section{Related Work}
	Accessibility in visual-centric games is getting more important and the game industry have to keep up implementing them.
	The research paper \textcite{goncalves_my_2023} has shown us that there are still major challenges to improve and further enhance existing accessibility features in various themes.
	In 2008 \textcite{grammenos_game_2008} developed a game called \emph{Game Over!}, which is the first universally inaccessible game showing people how it is if a game is unplayable.
	Additionally, in 2018 \textcite{andrade_echo-house_2018} described a new method to explore a virtual environment by using echolocation.
	This section provides a deeper insight into these studies, how they approached the topic and what results they achieved.

	\subsection{Echolocation in games}
	Test

	\section{Conclusions and Further Work}
	%TODO
	A recap of the problem addressed and the proposed solution.
	The implications of your research for the gaming industry and the broader accessibility community.
	Any remaining challenges or unanswered questions that need to be addressed.
	Suggestions for future research directions or enhancements to your proposed idea.
	How your work contributes to advancing the state-of-the-art in accessibility technology for blind individuals playing digital games.
